### 2023-05-02 about/vita.tex
The Vigil

\leftright{\bf Probabilistic analysis of branching processes}{\bf May 2020 -- present}
\leftright{\sl Research group}{\sl McGill University}
\smallskip
Ongoing research on branching processes, headed by Luc Devroye. Studied estimation problems
on Galton-Watson trees. Attended informal seminars, discussing
various topics related to branching
processes and other topics in probability and combinatorics.
(Gave a presentation at six of these: one on root estimation in Galton-Watson
trees, two on generating functions and elementary analytic combinatorics, two on graph regularity, and
one concerning two of Erd\H os's proofs on prime numbers.)

@@

\starleftright{\bf After school care supervisor}{\bf January 2023 -- present}
\leftright{\bf Suzuki Charter School}{\sl Edmonton, AB, Canada}
\smallskip
Supervise and facilitate activities (e.g., arts and crafts, dodgeball, drawing/colouring) for children
in grades 1 through 6.
\medbreak

@@

\begingroup\frenchspacing
\fictioncount=1
\pubbegin F
\ficitem ``Mountain Pass,'' {\sl Prairie Journal of Canadian Literature} {\bf 79} (2023), 48--55.
\endgroup%end the frenchspacing

@@

\parindent=10pt
\thing Recipient of 0x\$3.40 in Knuth reward cheques.
\smallskip
\thing Contributed sequences A335562, A338550, A338993, A339941, A339942, A341822, and A347580
to the On-line Encyclopedia of Integer Sequences.
\medbreak

>>>>

\leftright{\bf Probabilistic analysis of branching processes}{\bf May 2020 -- June 2022}
\leftright{\sl Research group}{\sl McGill University}
\smallskip
Research on branching processes, headed by Luc Devroye. Studied estimation problems
on Galton-Watson trees. Attended informal seminars, discussing
various topics related to branching
processes and other topics in probability and combinatorics.
(Gave a presentation at six of these: one on root estimation in Galton-Watson
trees, two on generating functions and elementary analytic combinatorics, two on graph regularity, and
one concerning two of Erd\H os's proofs on prime numbers.)

@@

\starleftright{\bf After school care supervisor}{\bf January 2023 -- present}
\leftright{\bf Suzuki Charter School}{\sl Edmonton, AB, Canada}
\smallskip
Supervise and facilitate activities (e.g., arts and crafts, soccer, board games, drawing/colouring) for children
in grades 1 through 6.
\medbreak

@@

\begingroup\frenchspacing
\fictioncount=2
\pubbegin F
\ficitem ``The Vigil,'' {\sl Ricepaper Magazine} (2023), online.
\ficitem ``Mountain Pass,'' {\sl Prairie Journal of Canadian Literature} {\bf 79} (2023), 48--55.
\endgroup%end the frenchspacing

@@

\parindent=10pt
\thing Recipient of 0x\$3.40 in Knuth reward cheques.
\smallskip
\thing Contributed sequences A335562, A338550, A338993, A339941, A339942, A341822, A347580,
A355145--A355147, and A360285
to the On-line Encyclopedia of Integer Sequences.
\medbreak
